---
title: "Speedup and Scaleup Analysis"
author: "Andres Calderon"
date: '`r Sys.Date()`'
output:
  html_document: default
  pdf_document: default
---

[//]: # ( Speedup )

#### Speedup for Berlin dataset.

We used the dataset built with SUMO using the Berlin network.  The size of the dataset is around 160K trajectories.  For speedup, a single timeslot was used with 160256 points.  Three nodes were available, 5 cores each.

```{r SpeedupSetup, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(ggplot2, data.table, foreach, sqldf)

PHD_HOME = Sys.getenv(c("PHD_HOME"))
PATH = "Y2Q4/Results/Speedup/"
filename ="Berlin_N160K-160K_E10.0-100.0"
files = system(paste0("ls ",PHD_HOME,PATH,filename,"_C1_*.csv"), intern = T)
core1 = data.frame()
foreach(f = files) %do% {
  core1 = rbind(core1, read.csv(f, header = F))
}
core1 = core1[, c(2, 3, 5, 6)]
names(core1) = c("Epsilon", "Dataset", "TimeA", "TimeB")
core1$Time1 = core1$TimeA + core1$TimeB
core1 = sqldf("SELECT Epsilon, Dataset, AVG(Time1) AS Time1 FROM core1 GROUP BY 1, 2")

files = system(paste0("ls ",PHD_HOME,PATH,filename,"_C*.csv"), intern = T)
data = data.frame()
foreach(f = files) %do% {
  data = rbind(data, read.csv(f, header = F))
}
data = data[, c(2, 3, 5, 6, 7)]
names(data) = c("Epsilon", "Dataset", "TimeA", "TimeB", "Cores")
data$Time = data$TimeA + data$TimeB
data = sqldf("SELECT Epsilon, Dataset, Cores, AVG(Time) AS Time FROM data GROUP BY 1, 2, 3")
#data = sqldf("SELECT Epsilon, Dataset, Cores, Time1/Time AS Speedup FROM data NATURAL JOIN core1")
data$Cores = factor(data$Cores)

data = data[data$Epsilon > 10, ]
```

```{r SpeedupPlot, echo=FALSE, fig.width=10.5, fig.height=7.5, fig.align='center'}
temp_title = paste("(radius of disk in mts) in Berlin dataset.")
title = substitute(paste("Speedup by ", epsilon) ~ temp_title, list(temp_title = temp_title))
g = ggplot(data=data, aes(x=factor(Epsilon), y=Time, fill=Cores)) +
  geom_bar(stat="identity", position=position_dodge(width = 0.75),width = 0.75) +
  labs(title=title, y="Time(s)", x=expression(paste(epsilon,"(mts)")))
plot(g)
```

#### Speedup on a Single Node.

```{r SpeedupSingleNodeSetup, include=FALSE}
PATH = "Y2Q4/Results/SpeedupSingleNode/"
filename ="Berlin_N160K-160K_E10.0-100.0"
files = system(paste0("ls ",PHD_HOME,PATH,filename,"_C*.csv"), intern = T)
data = data.frame()
foreach(f = files) %do% {
  data = rbind(data, read.csv(f, header = F))
}
data = data[, c(2, 3, 5, 6, 7)]
names(data) = c("Epsilon", "Dataset", "TimeA", "TimeB", "Cores")
data$Time = data$TimeA + data$TimeB
data = sqldf("SELECT Epsilon, Dataset, Cores, AVG(Time) AS Time FROM data GROUP BY 1, 2, 3")
#data = sqldf("SELECT Epsilon, Dataset, Cores, Time1/Time AS Speedup FROM data NATURAL JOIN core1")
data$Cores = factor(data$Cores)

data = data[data$Epsilon > 10, ]
```

```{r SpeedupSingleNodePlot, echo=FALSE, fig.width=10.5, fig.height=7.5, fig.align='center'}
temp_title = paste("(radius of disk in mts) in Berlin dataset.")
title = substitute(paste("Speedup by ", epsilon) ~ temp_title, list(temp_title = temp_title))
g = ggplot(data=data, aes(x=factor(Epsilon), y=Time, fill=Cores)) +
  geom_bar(stat="identity", position=position_dodge(width = 0.75),width = 0.75) +
  labs(title=title, y="Time(s)", x=expression(paste(epsilon,"(mts)")))
plot(g)
```

[//]: # ( Scaleup )

#### Scaleup for Berlin dataset.
Similar dataset was used to run scaleup analysis.  The 160K points were divided on three samples.  First one collected 1/3 of the data (small), second one 2/3 (medium) and third one keep the full content (full). The small sample was run using just one node (five cores). The medium dataset used 2 nodes (10 cores) and, finally, the full dataset run over the three available nodes. 

```{r ScaleupSetup, include=FALSE}
PATH = "Y2Q4/Results/Scaleup2/"
filename ="Berlin_N50K-150K_E10.0-100.0"

files = system(paste0("ls ",PHD_HOME,PATH,filename,"_C*.csv"), intern = T)
data = data.frame()
foreach(f = files) %do% {
  data = rbind(data, read.csv(f, header = F))
}
data = data[, c(2, 3, 5, 6, 7)]
names(data) = c("Epsilon", "Dataset", "TimeA", "TimeB", "Cores")
data$Time = data$TimeA + data$TimeB
data = sqldf("SELECT Epsilon, Dataset, Cores, AVG(Time) AS Time FROM data GROUP BY 1, 2, 3")
data05 = sqldf("SELECT Epsilon, Dataset, Cores, Time FROM data WHERE Dataset LIKE '50K' AND Cores = 5")
data10 = sqldf("SELECT Epsilon, Dataset, Cores, Time FROM data WHERE Dataset LIKE '100K' AND Cores = 10")
data15 = sqldf("SELECT Epsilon, Dataset, Cores, Time FROM data WHERE Dataset LIKE '150K' AND Cores = 15")
data = rbind(data05, data10, data15)
data$Cores = factor(data$Cores)
data = data[data$Epsilon > 10, ]
```

```{r ScaleupPlot, echo=FALSE, fig.width=10.5, fig.height=7.5, fig.align='center'}
temp_title = paste("(radius of disk in mts) in Berlin dataset.")
title = substitute(paste("Scaleup by ", epsilon) ~ temp_title, list(temp_title = temp_title))
g = ggplot(data=data, aes(x=factor(Epsilon), y=Time, fill=Cores)) +
  geom_bar(stat="identity", position=position_dodge(width = 0.75),width = 0.75) +
  labs(title=title, x=expression(paste(epsilon,"(mts)")))
plot(g)
```