---
title: "Execution time and Scaleup Analysis"
author: "Andres Calderon"
date: '`r Sys.Date()`'
output:
  html_document: default
  pdf_document: default
---

[//]: # ( Execution time )

#### Execution time for Berlin dataset.

We used the dataset built with SUMO using the Berlin network.  The size of the dataset is around 80K trajectories.  For speedup, a single timeslot was used with 80000 points.  Four nodes were available, 7 cores each.

```{r SpeedupSetup, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(ggplot2, data.table, foreach, sqldf)

PHD_HOME = Sys.getenv(c("PHD_HOME"))
PATH = "Y3Q1/Scripts/Speedup/"
filename ="Berlin_N80K-80K_E50.0-100.0"
files = system(paste0("ls ",PHD_HOME,PATH,filename,"_C*.csv"), intern = T)
data = data.frame()
foreach(f = files) %do% {
  data = rbind(data, read.csv(f, header = F))
}
data = data[, c(2, 3, 6, 9)]
names(data) = c("Epsilon", "Dataset", "Time", "Cores")
data = sqldf("SELECT Epsilon, Dataset, Cores, AVG(Time) AS Time FROM data GROUP BY 1, 2, 3")
data$Cores = factor(data$Cores)

data = data[data$Epsilon > 50, ]
```

```{r SpeedupPlot, echo=FALSE, fig.width=10.5, fig.height=7.5, fig.align='center'}
temp_title = paste("(radius of disk in mts) in Berlin dataset.")
title = substitute(paste("Execution time by ", epsilon) ~ temp_title, list(temp_title = temp_title))
g = ggplot(data=data, aes(x=factor(Epsilon), y=Time, fill=Cores)) +
  geom_bar(stat="identity", position=position_dodge(width = 0.75),width = 0.75) +
  labs(title=title, y="Time(s)", x=expression(paste(epsilon,"(mts)")))
plot(g)
```

#### Execution time on a Single Node.

```{r SpeedupSingleNodeSetup, include=FALSE}
PATH = "Y3Q1/Scripts/SpeedupSingleNode/"
filename ="Berlin_N80K-80K_E50.0-100.0"
files = system(paste0("ls ",PHD_HOME,PATH,filename,"_C*.csv"), intern = T)
data = data.frame()
for(i in 1:length(files)){
  data = rbind(data, read.csv(files[i], header = F))
}
data = data[, c(2, 3, 6, 9)]
names(data) = c("Epsilon", "Dataset", "Time", "Cores")
data = sqldf("SELECT Epsilon, Dataset, Cores, AVG(Time) AS Time FROM data GROUP BY 1, 2, 3")
data$Cores = factor(data$Cores)

data = data[data$Epsilon > 50, ]
```

```{r SpeedupSingleNodePlot, echo=FALSE, fig.width=10.5, fig.height=7.5, fig.align='center'}
temp_title = paste("(radius of disk in mts) in Berlin dataset.")
title = substitute(paste("Execution time by ", epsilon) ~ temp_title, list(temp_title = temp_title))
g = ggplot(data=data, aes(x=factor(Epsilon), y=Time, fill=Cores)) +
  geom_bar(stat="identity", position=position_dodge(width = 0.75),width = 0.75) +
  labs(title=title, y="Time(s)", x=expression(paste(epsilon,"(mts)")))
plot(g)
```

[//]: # ( Scaleup )

#### Scaleup for Berlin dataset.
Similar dataset was used to run scaleup analysis.  The 80K points were divided on four samples.  First one collected 1/4 of the data, second one 1/2, third one collected 3/4 and finally the last one kept the full content. The small sample was run using just one node (seven cores). The next sample used 2 nodes (14 cores).  Similarly, the third sample run over 3 nodes (21 cores) and, finally, the full dataset run over the four available nodes. 

```{r ScaleupSetup, include=FALSE}
PATH = "Y3Q1/Scripts/Scaleup/"
filename ="Berlin_N20K-80K_E50.0-100.0"

files = system(paste0("ls ",PHD_HOME,PATH,filename,"_C*.csv"), intern = T)
data = data.frame()
foreach(f = files) %do% {
  data = rbind(data, read.csv(f, header = F))
}
data = data[, c(2, 3, 6, 9)]
names(data) = c("Epsilon", "Dataset", "Time", "Cores")
data20 = sqldf("SELECT Epsilon, Dataset, Cores, Time FROM data WHERE Dataset LIKE '20K' AND Cores = 7")
data40 = sqldf("SELECT Epsilon, Dataset, Cores, Time FROM data WHERE Dataset LIKE '40K' AND Cores = 14")
data60 = sqldf("SELECT Epsilon, Dataset, Cores, Time FROM data WHERE Dataset LIKE '60K' AND Cores = 21")
data80 = sqldf("SELECT Epsilon, Dataset, Cores, Time FROM data WHERE Dataset LIKE '80K' AND Cores = 28")
data = rbind(data20, data40, data60, data80)
data = sqldf("SELECT Epsilon, Dataset, Cores, AVG(Time) AS Time FROM data GROUP BY 1, 2, 3")
data$Cores = factor(data$Cores)
data = data[data$Epsilon > 50, ]
```

```{r ScaleupPlot, echo=FALSE, fig.width=10.5, fig.height=7.5, fig.align='center'}
temp_title = paste("(radius of disk in mts) in Berlin dataset.")
title = substitute(paste("Scaleup by ", epsilon) ~ temp_title, list(temp_title = temp_title))
g = ggplot(data=data, aes(x=factor(Epsilon), y=Time, fill=Cores)) +
  geom_bar(stat="identity", position=position_dodge(width = 0.75),width = 0.75) +
  labs(title=title, y="Time(s)", x=expression(paste(epsilon,"(mts)")))
plot(g)
```
