\documentclass[12pt]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[square]{natbib}
\usepackage{url}
\usepackage{graphicx}

%opening
\title{Towards Parallel Detection of Moving Flock Patterns in Large Spatio-temporal Datasets\\ \normalsize{Report Outline}}
\author{Andres Calderon}

\begin{document}

\maketitle
 
\section{Introduction}
In this section I plan to discuss background information and motivation about the topic.  Importance of trajectory datasets and complex motion patterns will be discussed.  I would like to introduce the notion of moving flock patterns and the challenges to find the set of disks together with some basic definitions.

\section{Related Work}
Some work about spatio-temporal patterns will be revisited in order to introduce some seminal work about moving flock patterns.  BFE algorithm must be presented in this section.  Similarly, I would like to discuss some advances in spatial data analysis tools in distributed platforms (in particular Simba).

\section{Finding disks in parallel}
I plan to explain the details of the algorithm implemented in Simba and how some spatial predicates introduced by it can leverage the finding of disks.

\section{Experiments}
The setup and details about the datasets I plan to use will be discussed in this section.  It will show some figures comparing the implementation with a sequential version of the algorithm.

\section{Conclusions and Future Work}
I will share the lessons learned during the project and some future ideas to continue with the research.

% \bibliographystyle{plainnat}
% \bibliography{proposal}

\end{document}
