\documentclass[a4paper,10pt]{scrartcl}
\usepackage[hmargin=2.5cm,vmargin=3cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
colorlinks=false,
hidelinks
}

\setlength{\parindent}{2em}
\setlength{\parskip}{0.5em}

%opening
\title{Paper Review 3}
\author{Andres Calderon - SID:861243796}

\begin{document}
\maketitle
\thispagestyle{empty}

\section*{Stable Internet Routing Without Global Coordination (Gao and Rexford, 2001)}
The paper discusses the role of an Autonomous System (AS) in Internet Routing through three particular guidelines.  It uses the Border Gateway Protocol (BGP) to support ASs in the setting of their routing policies.  The authors claim that following these set of policies, route convergence is guaranteed.

The paper starts defining basic concepts around BGP as an interdomain routing protocol and important issues around route divergence.  The figures on the paper are useful to better understand the details of the hierarchical relationships between ASs and BGP routing. Then, the policy guidelines are explained with more formal definitions and theorems and their corresponding proofs.  Again, the figures and examples make a little bit easier the understanding of the ideas.  Overall, I think it is a well-organized and supported paper.


% \begin{thebibliography}{9}
% \bibitem{github} 
% Andres Calderon.
% \textit{GitHub Personal Repository}, 2015. 
% \url{https://github.com/aocalderon/PhD/tree/master/Y1Q1/GPU/lab3}.
% \end{thebibliography}

\end{document}
